### 2020-09-15 Analysis/Code/Paper.Rmd
Added tests for average review probabilities.

It is instructive to look at the results through the lens of stylized model introduced earlier in the section. Take the products close to a review upgrade first. For such products to choose to not go on a discount, the downside risk of doing so should be high, or they must have enough reviews to make changing their review score infeasible. Both scenarios would appear to be relatively unrealistic ex ante, and my results for firms on the verge of a positive transition comply with that expectation. On the other hand, the predictions for games that are close to a review downgrade were more blurred. It is reasonable to expect such products to dislike variance, unless the upside risk is strong. That would be the case reviews left during a discount are more positive, or if better review labels increase sales by a lot.

@@

```{r}
panel[, disc:=c(shift((discount > 0))), by = ID]
panel[, lam:=shift(lambda), by = ID]
panel[is.na(pReviews), pReviews := 0]
panel[is.na(nReviews), nReviews := 0]

revs <- panel[!(is.na(lam)), .(t, disc, lam, l = c(pReviews[1], diff(pReviews)), d = c(nReviews[1], diff(nReviews))), by=ID]

revs.lik <- function(x){
  revs[, r.plus := x[1] + disc*x[2], by = ID]
  revs[, r.minus := x[3] + disc*x[4], by = ID]

@@

library(nloptr)

x0 <- c(0.25, 0.0, 0.05, 0.0)
max.lik <- nloptr(x0, 
                  revs.lik,
                  lb = c(0, -1, 0, -1),
                  ub = c(10, 2, 10, 2),
                  opts = list(algorithm = "NLOPT_LD_LBFGS"))

x <- max.lik$solution
```

>>>>

It is instructive to look at the results through the lens of stylized model introduced earlier in the section. Take the products close to a review upgrade first. For such products to choose to not go on a discount, the downside risk of doing so should be high, or they must have enough reviews to make changing their review score infeasible. Both scenarios would appear to be relatively unrealistic ex ante, and my results for firms on the verge of a positive transition comply with that expectation. On the other hand, the predictions for games that are close to a review downgrade were more blurred. It is reasonable to expect such products to dislike variance, unless the upside risk is strong. That would be the case if reviews left during a discount were more positive, or if better review labels increased sales by a lot.

@@

```{r}
# In this module I estimate the average like and dislike rates on and off discount,
# and I test whether: (a) users leave better reviews on a discount, (b) users leave
# more reviews during discounts
panel[, disc:=c(shift((discount > 0))), by = ID]
panel[, lam:=shift(lambda), by = ID]
panel[is.na(pReviews), pReviews := 0] # remove this, it is already in CreateSample
panel[is.na(nReviews), nReviews := 0] # remove this, it is already in CreateSample

# part of the panel that has new reviews and estimated arrivals
revs <- panel[!(is.na(lam)), .(t, disc, lam, l = c(pReviews[1], diff(pReviews)), d = c(nReviews[1], diff(nReviews))), by=ID]

# negative of the likelihood function
revs.lik <- function(x){
  revs[, r.plus := x[1] + disc*x[2], by = ID]
  revs[, r.minus := x[3] + disc*x[4], by = ID]

@@

# maximize the likelihood to estimate the parameters
library(nloptr)
x0 <- c(0.25, 0.0, 0.05, 0.0)
max.lik <- nloptr(x0, 
                  revs.lik,
                  lb = c(0, -1, 0, -1),
                  ub = c(10, 2, 10, 2),
                  opts = list(algorithm = "NLOPT_LD_LBFGS"))

theta <- max.lik$solution

# Estimate E[score score']
sigma.hat <- function(x){
  revs[, r.plus := x[1] + disc*x[2]]
  revs[, r.minus := x[3] + disc*x[4]]

  dt <- revs[, .(s1 = l/r.plus - lam, s2 = (l/r.plus - lam)*disc,
                 s3 = d/r.minus - lam, s4 = (d/r.minus - lam)*disc)]

  (as.matrix(transpose(dt)) %*% as.matrix(dt))/(dim(revs)[1]) %>%
    return()
}

# Estimate the hessian d(score)/d theta'
H.hat <- function(x){
  n <- dim(revs)[1]
  revs[, r.plus := x[1] + disc*x[2]]
  revs[, r.minus := x[3] + disc*x[4]]

  H <- matrix(rep(0, length(x)*length(x)), nrow = length(x))

  h <- revs[, .(h11 = -l/(r.plus)^2, h12 = -l/(r.plus)^2*disc, h13 = 0, h14 = 0,
           h21 = -l/(r.plus)^2*disc, h22 = -l/(r.plus)^2*disc^2, h23=0, h24 = 0,
           h31 = 0, h32 = 0, h33 = -d/(r.minus)^2, h34 = -d/(r.minus)^2*disc,
           h41 = 0, h42 = 0, h43 = -d/(r.minus)^2*disc, h44 = -d/(r.minus)^2*disc^2)]

  for (i in 1:n){
    hi <- h[i] %>% as.matrix() %>% matrix(., nrow =  length(x))
    H <- H + hi
  }

  return(H/n)
}

# calculate the variance-covariance matrix of theta hat (divided by n)
sigma <- sigma.hat(theta)
H <- H.hat(theta)
H.inv <- solve(H, diag(1, nrow = 4))
omega <- (H.inv %*% sigma %*% H.inv) / dim(revs)[1]

# Test if the probability to leave a review goes up: 
# a(theta) = theta2 + theta4
# Null: a(theta_0) = 0
A <- matrix(c(0,1,0,1), nrow = 4)
# t stat
(theta[2] + theta[4])/sqrt(t(A) %*% omega %*% A)

# Test if the probability to leave a like conditional on review (score) goes up
# with a discount
# a(theta) = (theta[1] + theta[3])/(sum(theta)) - theta[1]/(theta[1] + theta[3])
grad.a <- function(x){

  sum.x <- sum(x)

  A1 <- (sum.x - x[1]) / (sum.x)^2 - x[3]/(x[1] + x[3])^2
  A2 <- (sum.x - x[2]) / (sum.x)^2
  A3 <- (- x[1] - x[2]) / (sum.x)^2  + x[1]/(x[1] + x[3])^2
  A4 <- (- x[1] - x[2]) / (sum.x)^2

  return(c(A1, A2, A3, A4))
}

A <- grad.a(theta)

score.dif <- (theta[1] + theta[2])/(sum(theta)) - (theta[1])/(theta[1] + theta[3])

score.dif/sqrt(t(A) %*% omega %*% A)
```
